Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-16 paper.tex
Reword C_D results

The behavior of the mean rotor drag coefficient $C_D$ is similar, though the
changes are less dramatic. This is likely due to cross-flow turbine geometry,
where increases in blade drag at lower $Re$ somewhat offsets the reduction in
lift, to keep total streamwise force from changing as much as the rotor torque.
The tendency for $C_D$ to continue increasing with $Re$ may also include the
effects of an increasing Froude number, which increases free surface deformation
and wave drag during towing without increasing flow through the turbine.

>>>>

The behavior of the mean rotor drag coefficient $C_D$ is similar, though the
changes are less dramatic. This is likely due to cross-flow turbine geometry,
where increases in blade drag at lower $Re$ somewhat offsets the reduction in
lift, causing the total streamwise force to vary less than the rotor torque. The
tendency for $C_D$ to continue increasing with $Re$ may also include the effects
of an increasing Froude number, which increases free surface deformation and
wave drag during towing without increasing flow through the turbine.
